
\begin{framed}
 \begin{tcolorbox}
   \begin{center} 
     Overview of Facilities and Surveys related to this proposal
   \end{center}
 \end{tcolorbox}
  
\noindent
\textbf{\textsc{Imminent:}}

The {\bf Sloan Digital Sky Survey (SDSS):} An ongoing project,
currently in its fourth phase, SDSS-IV.  {\bf The PI was a leading
member of the SDSS-III: Baryon Oscillation Spectroscopic Survey (BOSS;
see Track Record and C.V.).} The fifth generation of Sloan Digital Sky
Surveys, SDSS-V will be an all-sky, multi-epoch spectroscopic survey,
yielding spectra of over 6 million objects during its lifetime. In
particular, the SDSS-V Black Hole Mapper (BHM) will focus on
long-term, time-domain studies of AGN, including direct measurement of
black hole masses and changing-look quasars, and on the optical
characterization of eROSITA X-ray sources. Data taking for SDSS-V is due to start
in 2020.  {\it Data Products: Repeat spectra
in the North and Southern Hemisphere for 500,000 bright QSOs.} \\

The {\bf Dark Energy Spectroscopic Instrument (DESI) Survey:} is a 5
year cosmology survey that will be conducted on the Mayall 4-meter
telescope at Kitt Peak National Observatory starting in 2019. It uses
the 5,000 fiber Dark Energy Spectroscopic Instrument and will obtain
optical spectra for $\approx$20 million galaxies and quasars.  {\bf
The PI contributed in writing the original science case and proposal
for DESI \citep{Schlegel2011} but having left the U.S./LBNL, he no
longer has data access rights.}  {\it Data Products: Spectra of 1e6
quasars across 14,000 deg$^{2}$ of the Northern Sky.} \\

The {\bf Large Synoptic Survey Telescope (LSST)} project starts data
taking in late 2021, and and will conduct a full survey of the
Southern Sky every 3 nights. The LSST survey is designed to address
four science areas (Understanding the Mysterious Dark Matter and Dark
Energy; Hazardous Asteroids and the Remote Solar System; The Transient
Optical Sky; The Formation and Structure of the Milky Way) and is an
absolutely unique facility as far as areal, temporal and wavelength
coverage. The U.K.  is a member of LSST giving me free data access
rights, (but to the raw, unfiltered data).  {\it Data Products:
$ugrizY$ broadband optical and near-infrared imaging for 20,000
deg$^2$.  Images the full Southern Sky every 3 days.} \\

\textit{\textbf{Euclid}} is an ESA Medium Class mission due for launch
in mid-2021 that will map the geometry of the dark Universe.  It aims
to understand why the expansion of the Universe is accelerating and
what the nature of the source responsible for this acceleration
(``dark energy'') is.  The mission will investigate the
distance-redshift relationship and the evolution of cosmic structures
by measuring shapes and redshifts of galaxies and clusters of galaxies
out to redshifts $\sim$2, or equivalently to a look-back time of 10
billion years. {\it Euclid} will also discover a range of
near-infrared (NIR) detected quasars, {\it Euclid} is planned for
launch in mid-2021.  {\it Data Products: Very broadband optical and 3
filter near-infrared space-based imaging for 15,000 deg$^2$.} \\

The {\bf 4-metre Multi-Object Spectroscopic Telescope (4MOST):} is a
fibre-fed spectroscopic survey facility on the VISTA telescope with a
large enough field-of-view to survey a large fraction of the southern
sky. The facility will be able to simultaneously obtain spectra of
2,400 objects distributed over a field-of-view of 4 square degrees.
The initial Galactic and Extragalactic surveys will operate over a
five-year period delivering spectra for $\geq$25 million objects over
$\gtrsim$15,000 deg. 4MOST will commence science operations in early
2022. {\it Data Products: } 4MOST will operate continuously for an
initial five-year public survey delivering spectra for $\geq$25
million object over 15,000 deg$^{2}$.\\

The {\bf James Webb Space Telescope (JWST)} is a space telescope
developed in coordination among NASA, the European Space Agency, and
the Canadian Space Agency. It is scheduled to be launched in June
2019. The telescope will offer unprecedented resolution and
sensitivity from 0.6 to 27$\mu$m. JWST is a partnership between NASA,
ESA and the Canadian Space Agency. In particular, ESA's contributions
to JWST include (but are not limited to) the NIRSpec instrument and
the Optical Bench Assembly of the MIRI instrument.  In return for
these contributions, ESA gains full partnership in JWST and secures
full access to the JWST observatory for astronomers from ESA Member
States on identical terms to those of today on the {\it Hubble Space
Telescope}. {\it Data Products: Revolutionary optical to mid-infrared
deep-field imaging and spectra.  Unique access to wavelengths
$\lambda>2\mu$m, inaccessible from the ground, ideal for high-$z$
quasar studies.} \\


The {\bf Extended Roentgen Survey with an Imaging Telescope Array
(eROSITA)} is the main instrument on the Spektr-RG mission, an
international high-energy astrophysics observatory.  Set to launch in
2019 with both high sensitivity and a large FOV, eROSITA will discover
as many new X-ray sources in its first twelve months as are known
today, after more than 50 years of X-ray astronomy.  SDSS-V will
provide optical spectroscopic measurements including identifications
and redshifts, of $\sim$400,000 eROSITA X-ray sources detected in the
first 1.5 years of the all sky survey.  In addition, SDSS-V's BHM will
characterize numerous serendipitous discoveries, extreme and rare
objects, transients, and other peculiar variables found in the eROSITA
survey \citep{Merloni2012}, and expand an optical+X-ray quasar sample
with implications for observational cosmological constraints
\citep[e.g.][]{Risaliti_Lusso2015}.\\

%\underline{Notes:} 4MOST has full access to the full LSST footprint. LSST will overlap half (7,500 deg$^2$) of the {\it Euclid} footprint. Data access to eROSITA sources is via an MOU with SDSS-V. \\

\end{framed}
