\documentclass[oneside, a4paper, onecolumn, 11pt]{article}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{sectsty}
\chapterfont{\color{blue}}  % sets colour of chapters
\sectionfont{\color{cyan}}  % Cerulean
\subsectionfont{\color{ProcessBlue}}  % MidnightBlue, CornflowerBlue, NavyBlue ProcessBlue

\input{format}

%\usepackage[left=2.05cm,top=2.05cm,bottom=1.55cm,right=2.05cm]{geometry}
\usepackage[left=2.05cm,top=2.05cm,right=2.05cm]{geometry}
\setlength{\bibsep}{0.0pt}


\tcbuselibrary{skins}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

\tcbset{tab1/.style={enhanced, fonttitle=\bfseries, fontupper=\normalsize\sffamily,
colback=yellow!10!white,
colframe=red!50!black,
colbacktitle=Cerulean!40!white,
coltitle=black,center title}
%subtitle style={boxrule=0.4pt, colback=yellow!50!red!25!white} 
}

%% To fix list things: 
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\renewcommand{\labelitemi}{\tiny$\blacksquare$}

\renewcommand{\thesection}{\alph{section}}
%\renewcommand{\thesubsection}{\Alph{subsection}}

\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0pt}  %% Remove line at top

%\pagestyle{empty}
\fancyhf{}
%\lhead{{\it ERC-2015-StG}}
%\lhead{{\it DEQUASARS: Part B1 }}
\lhead{{\it Ross}}
\chead{Part B2}
\rhead{Q4D}
\setcounter{page}{1}
\lfoot{{\it ERC-COG-2018}}
\rfoot{{\it Scientific Proposal}}
\cfoot{{\it Page \thepage\ of 15}}
%\rfoot{{\it FP7-PEOPLE-2013-IIF}}

\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}


\begin{document}

\begin{center}
{\Large \bf \textcolor{Cerulean}{Q4D: Quasars in the 4th Dimension\\}}
%\vspace{4pt} 
 %{\Large \bf \textcolor{Cerulean}{the new field of Extragalactic Variable Astrophysics} }
\end{center}
\vspace{-16pt} 


%\tableofcontents


%\medskip \medskip 
\medskip \medskip
%\begin{quotation}
\noindent
{\it 
All massive galaxies are thought to have supermassive black holes at
their centres, and to have undergone a ``quasar phase'' in
their past. Along with fusion in stars, accretion onto the central
supermassive black hole is the main energy source available to a
galaxy. However, we are missing a deep understanding of galaxy
formation theory since we still do not understand in key detail how
the energy associated with the quasar escapes the central engine to impact the host galaxy and
the intergalactic medium. Further issues arise since recent
observations of extreme variability in quasars have broken standard
viscous accretion disk models.

\smallskip
\smallskip
\noindent
In this proposal, we propose the ground breaking idea of combining the
data from several next-generation state-of-the art surveys (SDSS-V,
DESI, LSST, 4MOST, ESA {\it Euclid} and JWST) in order to go beyond
the state-of-the-art and construct the extragalactic dataset with the
crucial time-domain aspect that is necessary to address the current
challenges.  The experience of the P.I., along with the strategic
data nexus aspect of the Royal Observatory at the University of
Edinburgh makes my group uniquely placed to address and answer this
problem.  The goal is to create a holistic theory of accretion disk
physics and quasar feedback in galaxy formation theory. We are also
extremely well placed to discover brand new extragalactic variable
phenomena.
}
%\end{quotation}
\vspace{-20pt}


\input{objectives}


\input{methodology}


\input{resources}


\newpage
%%\thispagestyle{empty}
\fancyhf{}
%\lhead{{\it ERC-2018-CoG}}
%\lhead{{\it DEQUASARS: Part B1 }}
\lhead{{\it Ross}}
\chead{Part B2}
\rhead{Q4D}
\setcounter{page}{1}
\lfoot{{\it ERC-COG-2018}}
\rfoot{{\it Scientific Proposal}}
%\cfoot{{\it Page \thepage\ of 5}}

%\input{references}
\bibliographystyle{plainnat}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}




\end{document}

