
\begin{framed}
 \begin{tcolorbox}
   \begin{center} 
     Overview of Facilities and Surveys related to this proposal
   \end{center}
 \end{tcolorbox}
  
\noindent
\textbf{\textsc{Imminent:}}

The {\bf Sloan Digital Sky Survey (SDSS):} An ongoing project,
currently in its fourth phase, SDSS-IV.  {\bf The PI was a leading
member of the SDSS-III: Baryon Oscillation Spectroscopic Survey (BOSS;
see Track Record and C.V.).} The fifth generation of Sloan Digital Sky
Surveys, SDSS-V will be an all-sky, multi-epoch spectroscopic survey,
yielding spectra of over 6 million objects during its lifetime. In
particular, the SDSS-V Black Hole Mapper (BHM) will focus on
long-term, time-domain studies of AGN, including direct measurement of
black hole masses and Changing-Look quasars, and the optical
characterization of eROSITA X-ray sources. Data taking for SDSS-V is due to start
in 2020.  {\it Data Products: Multiple repeat spectra
in the North and Southern Hemisphere for 500,000 quasars.} \\

The {\bf Dark Energy Spectroscopic Instrument (DESI) Survey} is a 5
year cosmology survey that will be conducted on the Mayall 4-meter
telescope at Kitt Peak National Observatory starting in late 2019. It uses
the 5,000 fiber Dark Energy Spectroscopic Instrument and will obtain
optical spectra for $\approx$20 million galaxies and quasars.  {\bf
The PI contributed in writing the original science case and proposal
for DESI \citep{Schlegel2011} but having left the U.S./LBNL, he no
longer has data access rights.}  {\it Data Products: Spectra of 1e6
quasars across 14,000 deg$^{2}$ of the Northern Sky.} \\

The {\bf Large Synoptic Survey Telescope (LSST)} project starts data
taking in late 2021, and will conduct a full survey of the
Southern Sky every 3 nights. The LSST survey is designed to address
four science areas (Understanding Dark Matter and Dark
Energy; Hazardous Asteroids and the Remote Solar System; The Transient
Optical Sky; The Formation and Structure of the Milky Way) and is an
absolutely unique facility as far as areal, temporal and wavelength
coverage. The U.K.  is a member of LSST giving me free data access
rights (to the raw, unfiltered data).  {\it Data Products:
$ugrizY$ broadband optical and near-infrared imaging for 20,000
deg$^2$.  Images the full Southern Sky every 3 days.} \\
%% LSST:: Each patch of sky it images will be visited 1000 times during the survey,


\textit{\textbf{Euclid}} is an ESA Medium Class mission due for launch
in mid-2021 that will map the geometry of the dark Universe.  It aims
to understand why the expansion of the Universe is accelerating and
what the nature of the source responsible for this acceleration
(``dark energy'') is.  The mission will investigate the
distance-redshift relationship and the evolution of cosmic structures
by measuring shapes and redshifts of galaxies and clusters of galaxies
out to redshifts $\sim$2, or equivalently to a look-back time of 10
billion years. {\it Euclid} will also discover a range of
near-infrared (NIR) detected quasars, {\it Euclid} is planned for
launch in mid-2021.  {\it Data Products: Very broadband optical and 3
filter near-infrared space-based imaging for 15,000 deg$^2$, 
overlapping SDSS-V in the North and LSST in the South.} \\

The {\bf 4-metre Multi-Object Spectroscopic Telescope (4MOST):} is a
fibre-fed spectroscopic survey facility on the VISTA telescope with a
large field-of-view in order to survey a large fraction of the Southern
sky. The facility will be able to simultaneously obtain spectra of
2,400 objects distributed over a field-of-view of 4 deg$^{2}$.
The initial Galactic and Extragalactic surveys will operate over a
five-year period delivering spectra for $\geq$25 million objects over
$\gtrsim$15,000 deg$^{2}$. 4MOST will commence science operations in early
2022. {\it Data Products: } 4MOST will operate continuously for an
initial five-year public survey delivering spectra for $\geq$25
million object over 15,000 deg$^{2}$.\\

The \textbf{\emph{James Webb Space Telescope} (JWST)} is a space
telescope developed in coordination among NASA, ESA and the Canadian
Space Agency. It is scheduled to be launched in June 2019. The
telescope will offer unprecedented resolution and sensitivity from 0.6
to 27$\mu$m. ESA's contributions to JWST include (but are not limited
to) the NIRSpec instrument and the Optical Bench Assembly of the MIRI
instrument.  In return for these contributions, ESA gains full
partnership in JWST and secures full access to the JWST observatory
for astronomers from ESA Member States. {\it Data Products:}
Revolutionary optical to mid-infrared deep-field imaging and spectra.
Unique access to wavelengths $\lambda>2\mu$m, inaccessible from the
ground, ideal for high-$z$ quasar studies. \\


The {\bf Extended Roentgen Survey with an Imaging Telescope Array
(eROSITA)} is the main instrument on the Spektr-RG mission, an
international high-energy astrophysics observatory.  Set to launch in
2019 with both high sensitivity and a large FOV, eROSITA will discover
as many new X-ray sources in its first twelve months as are known
today, after more than 50 years of X-ray astronomy.  SDSS-V will
provide optical spectroscopic measurements including identifications
and redshifts, of $\sim$400,000 eROSITA X-ray sources detected in the
first 1.5 years of the all sky survey.  In addition, SDSS-V's BHM will
characterize numerous serendipitous discoveries, extreme and rare
objects, transients, and other peculiar variables found in the eROSITA
survey \citep{Merloni2012}, and expand an optical+X-ray quasar sample
with implications for observational cosmological constraints
\citep[e.g.][]{Risaliti_Lusso2015}.\\

%\underline{Notes:} 4MOST has full access to the full LSST footprint. LSST will overlap half (7,500 deg$^2$) of the {\it Euclid} footprint. Data access to eROSITA sources is via an MOU with SDSS-V. \\
%\hrulefill 

\noindent
\textbf{\textsc{Ongoing:}} 

The {\bf Wide-field Infrared Survey Explorer (WISE)} is a NASA
infrared-wavelength astronomical space telescope launched in December
2009 and is still operation (as at the time of writing, in its
``NEOWISE-R'' mission phase). WISE performed an all-sky astronomical
survey with images at 3.4, 4.6, 12 and 22$\mu$m using a 40cm (16 in)
diameter infrared telescope in Earth orbit.  {\bf The P.I. is a world
expert in quasar identification using WISE \citep[e.g., ][]{Ross2012,
Ross2015, Timlin2016, Timlin2018} and exploiting mid-infrared light
curve data.} \\

The \textbf{ESA {\it Gaia}} mission is an ongoing mission to map 
the Milky Way in three-dimensions, in the process
revealing the composition, formation and evolution of the Galaxy. {\it Gaia} 
is providing unprecedented positional and radial velocity measurements
with the accuracies needed to produce a stereoscopic and kinematic
census of about $\sim$one billion stars in our Galaxy and throughout
the Local Group. This amounts to about 1 per cent of the Galactic
stellar population.

\end{framed}
