%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  https://tex.stackexchange.com/questions/337820/mcq-long-table-using-tikz-tcolorbox-or-tabular
%%  https://tex.stackexchange.com/questions/283419/color-in-a-multirow-cell-with-extra-vertical-space/283454
%%  https://tex.stackexchange.com/questions/406033/how-to-fit-a-cell-of-a-table-to-a-figure-and-arrange-multiple-tables/406042
%% 
%% THIS (??)::
%%     https://texblog.org/2014/05/19/coloring-multi-row-tables-in-latex/
%%
%%
%%   https://www.inf.ethz.ch/personal/markusp/teaching/guides/guide-tables.pdf
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{tcolorbox}[tab1, tabularx={X  X }, title=Outstanding Issues in Variable Extragalactic Astrophysics, boxrule=1.25pt] 
Key Objective                                                                            &  Investigation and Resolution      \\ 
\hline \hline
\multicolumn{2}{c}{{\sc The physics of accretion}} \\ 
Investigate ``hot'' and ``cold'' mode accretion in the quasar
population; determine the rates and timescales characterising the
Changing Look Quasar (CLQ) population.  &
Identify and characterize all the CLQs in DESI, SDSS-V, 4MOST and LSST
{\bf (WP1; WP3; WP4)}. \\
%%
\hline
Probe and determine the physical state of the inner parsec of the
quasar central engine.  & 
Rapid analysis and response for LSST quasar light curves {\bf (WP1; WP3)}.
Detailed accretion disk theoretical modeling {\bf (WP4)}. \\
\hline
%%
\multicolumn{2}{c}{{\sc Obscured accretion and galaxy formation}} \\
Establish the relative importance that major mergers, minor mergers,
cold streams and secular evolution have towards the growth of SMBHs
across cosmic time.  & 
Deep imaging data from LSST combined with searching for post-starburst
signatures in DESI, SDSS-V, 4MOST spectra. {\bf (WP1; WP2; WP3)} Also
NIRcam and MIRI imaging from JWST {\bf (WP5)}. \\ \hline
%%
Establish the bolometric output and origin of IR emission, and
determine presence of extreme outflows in the $z\sim2-3$ quasar
population. & 
NIRSpec and MIRI MRS spectroscopy with JWST {\bf (WP5)}. \\ \hline
%%
Establishing the range of SED parameter space the quasars occupy by a
multi-wavelength multi-epoch ``truth table dataset''. & 
Build ``The Quasar SED Rosetta Stone'' using X-ray, UV/optical, IR
data as well as repeat optical observations from LSST {\bf (WP1; WP2)}.
\\ \hline
%%
Discover the physical conditions under which SMBH grew at the epoch
when most of the accretion and star formation in the Universe occurred
($z\sim1-4$).  &
Perform a complete census of AGN across $z\sim0-8$, focussing on
$z=1-4$ using the very wide-field surveys to boost statistics for rare
objects and medium-deep multiwavelength datasets to sample the
faint-end of the luminosity function.  {\bf (WP2; WP3; WP5)} \\ \hline
%%
\multicolumn{2}{c}{{\sc Galaxy-scale feedback}}\\
Establish the theoretical impact of extreme outflows in the $z\sim2-3$ quasar population & 
Next-generation Hydro-simulation modelling {\bf (WP4)}.  \\
\hline
Understand how the accretion disks around black holes launch winds and outflows and determine how much energy these carry. 
Quantify the amount of ``Maintenance/Jet/Kinetic'' mode and ``Transition/Radiative/Wind'' mode feedback.
& 
Connect accretion disk theory and models to cosmolgocial-scale hydro simulations for 
a holistic theory of ``quasar feedback'' {\bf (WP4)}.  \\ 
    %\end{tcbitemize}
\end{tcolorbox}
