\documentclass[oneside, a4paper, onecolumn, 11pt]{article}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{sectsty}
\chapterfont{\color{blue}}                   % sets colour of chapters
\sectionfont{\color{cyan}}                   % Cerulean
\subsectionfont{\color{ProcessBlue}}  % MidnightBlue, CornflowerBlue, NavyBlue ProcessBlue

\input{format}

%\usepackage[left=2.05cm,top=2.05cm,bottom=1.55cm,right=2.05cm]{geometry}
\usepackage[left=2.05cm,top=2.05cm,right=2.05cm]{geometry}
\setlength{\bibsep}{0.0pt}


\tcbuselibrary{skins}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

\tcbset{tab1/.style={enhanced, fonttitle=\bfseries, fontupper=\normalsize\sffamily,
colback=yellow!10!white,
colframe=red!50!black,
colbacktitle=Cerulean!40!white,
coltitle=black,center title}
%subtitle style={boxrule=0.4pt, colback=yellow!50!red!25!white} 
}

%% To fix list things: 
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\renewcommand{\labelitemi}{\tiny$\blacksquare$}

\renewcommand{\thesection}{\alph{section}}
%\renewcommand{\thesubsection}{\alph{subsection}}

\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0pt}  %% Remove line at top
%\pagestyle{empty}
\fancyhf{}
\lhead{{\it Ross}}
\chead{Part B2}
\rhead{Q4D}
\setcounter{page}{1}
\lfoot{{\it ERC-COG-2018}}
\rfoot{{\it Scientific Proposal}}
\cfoot{{\it Page \thepage\ of 15}}

\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}


\begin{document}

\begin{center}
\large \textbf{ERC Consolidator Grant 2018} \\
\large \textbf{Research proposal [Part B2]}  \\
\large \textbf{\emph{(not evaluated in Step 1)}}
\end{center}


%\tableofcontents
\noindent
\textbf{\textcolor{Cerulean}{Part B2: \emph{\underline{The scientific proposal}} (max. 15 pages, references do not count towards the page limits)}}\\

\noindent
{\it 
All massive galaxies are thought to have supermassive black holes at
their centres, and to have undergone a ``quasar phase'' in their
past. Along with fusion in stars, accretion onto the central
supermassive black hole is the main energy source available to a
galaxy. However, we are missing a deep understanding of galaxy
formation theory since we still do not understand in key detail how
the energy associated with the quasar escapes the central engine to
impact the host galaxy and the intergalactic medium. Further issues
arise since recent observations of extreme variability where some
quasars show changes in luminosity and activity over the course of
weeks to years, have broken standard viscous accretion disk models.

\smallskip
\smallskip
\noindent
In Q4D we will address these outstanding issues in order to move the
field forward.  Q4D has several ambitious goals: {\it (i)} to characterize
the variable extragalactic universe and quasar population and in doing
so kick start the new field of variable extragalactic astrophysics;
{\it (ii)} to create a holistic theory of accretion disk physics and
quasar feedback in galaxy formation theory, and {\it (iii)} discover
brand new astronomical phenomena.

\smallskip
\smallskip
\noindent
We will achieve this by combining the data from several
next-generation state-of-the art surveys (SDSS-V, DESI, LSST, 4MOST,
ESA {\it Euclid} and JWST) in order to go beyond the state-of-the-art
and construct the extragalactic dataset with the crucial time-domain
aspect that is necessary to address the current challenges.  This will
allow substantial advances in the frontiers of understanding
astrophysical phenomena as well as discovering new objects.  The
experience of the PI (Nicholas P. Ross; NPR) along with the strategic
data nexus aspect of the Royal Observatory at the University of
Edinburgh makes my group uniquely positioned to address this problem
and carry out this research.  }


\vspace{-4pt}

\input{objectives}


\input{methodology}


\input{resources}


\newpage
%%\thispagestyle{empty}
\fancyhf{}
%\lhead{{\it ERC-2018-CoG}}
%\lhead{{\it DEQUASARS: Part B1 }}
\lhead{{\it Ross}}
\chead{Part B2}
\rhead{Q4D}
\setcounter{page}{1}
\lfoot{{\it ERC-COG-2018}}
\rfoot{{\it Scientific Proposal}}
%\cfoot{{\it Page \thepage\ of 5}}

%\input{references}
\bibliographystyle{plainnat}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}




\end{document}

